A Digital Library for Crowds on the Real-Time Social Web

### 2011-05-05 docs/csce_675/paper.tex
fixed minor bug - that crashed pdflatex
fixed spelling

\medskip Hence, we can take advantage of both, local changes to the overall
communication network (spatial locality) and recent changes to the network
(temporal locality), for supporting efficient transient crowd discovery. The complete algorithm is decsribed in \cite{Kamath:2011:TCD}

@@

\subsubsection{GeoStream}
This crawler listens to Twitter's
streaming API to find geo-located tweets.  It recieves every geo-located tweet
posted from anywhere in the world.  In the future, this data may be used to
show crowds on a map.

\subsection{Grouper}
Groupers detect crowds in the data collected by a crawler.  The precise
definition of a crowd depends on the implementation of the grouper.  A grouper
could create crowds based on comunication patterns, geographical proximity, or
textual similarity. Once crowds are discovered, this module formats crowds to a
well defined crowds object and adds it to a DBMS.

\subsubsection{Mentions}
For this project, we exclusivly discover crowds based on communication.  The
mentions grouper looks for sets of people who are communicating with each
other.  The algorithm to discover crowds is described in
Section~\ref{sec:crowd_algorithm}.

@@

\subsection{HTTP JSON RESTful APIs}: This module provides client an interface to the digital library. The module exposes JSON APIs that the clients can use to browse and search the crowds archive. Here is a brief description of the more important methods:
\begin{description}
 \item[search/crowd] Find crowds sorted by relevance or time.
 \item[crowd/id] Retrieve all of the data for a crowd.
 \item[crowd/users] Retrieve a list of all the users in the crowd.
 \item[crowd/tweets] Retrieve a list of all the tweets in the crowd.
 \item[crowd/star] Mark a crowd as significant.
 \item[user/edges] Retrieve the friend and follower relationships for a given user.
\begin{description}

>>>>

\medskip Hence, we can take advantage of both, local changes to the overall
communication network (spatial locality) and recent changes to the network
(temporal locality), for supporting efficient transient crowd discovery. The complete algorithm is described in \cite{Kamath:2011:TCD}

@@

\subsubsection{GeoStream}
This crawler listens to Twitter's
streaming API to find geo-located tweets.  It receives every geo-located tweet
posted from anywhere in the world.  In the future, this data may be used to
show crowds on a map.

\subsection{Grouper}
Groupers detect crowds in the data collected by a crawler.  The precise
definition of a crowd depends on the implementation of the grouper.  A grouper
could create crowds based on communication patterns, geographical proximity, or
textual similarity. Once crowds are discovered, this module formats crowds to a
well defined crowds object and adds it to a DBMS.

\subsubsection{Mentions}
For this project, we exclusively discover crowds based on communication.  The
mentions grouper looks for sets of people who are communicating with each
other.  The algorithm to discover crowds is described in
Section~\ref{sec:crowd_algorithm}.

@@

\subsection{HTTP JSON RESTful APIs}: This module provides client an interface to the digital library. The module exposes JSON APIs that the clients can use to browse and search the crowds archive. Here is a brief description of the more important methods:
\begin{description}
 \item[search/crowd] Find crowds sorted by relevance or time.
 \item[crowd/id] Retrieve all of the data for a crowd.
 \item[crowd/users] Retrieve a list of all the users in the crowd.
 \item[crowd/tweets] Retrieve a list of all the tweets in the crowd.
 \item[crowd/star] Mark a crowd as significant.
 \item[user/edges] Retrieve the friend and follower relationships for a given user.
\end{description}
